%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}

% Contact info, can exclude these assignments and update in external var.tex file
% \input{var.tex}
% current commands in var.tex
\newcommand{\firstLast}{Ryan Backman}
\newcommand{\phoneNumber}{123-456-7890}
\newcommand{\email}{example@email.com}
\newcommand{\github}{https://github.com/rbk6}
\newcommand{\linkedin}{https://www.linkedin.com/in/ryan-backman/}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large \firstLast} & email -- \href{mailto:\email}{\email}\\
  \href{\github}{\github} & mobile -- \phoneNumber \\
\end{tabular*}

% \begin{center}
%     \textbf{\Huge \scshape \firstLast} \\ \vspace{1pt}
%     \small \phoneNumber $|$ \href{mailto:{\email}}{\underline{\email}} $|$ 
%     \href{\linkedin}{\underline{\linkedin}} $|$
%     \href{\github}{\underline{\github}}
% \end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Nevada, Las Vegas}{Las Vegas, NV}
      {Bachelor of Science in Computer Science}{August 2019 -- May 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  % -----------Multiple Positions Heading-----------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 - Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd
  %  \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading%DONE
      {Software Development Engineer}{December 2023 -- Present}
      {Amazon}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Developed NICv2, an image evaluation tool, as part of the review process for images generated by a lifestyle imagery project, utilizing a Java REST API and React web application to enhance project management and visibility into evaluation statistics.}
        \resumeItem{Implemented a scheduled incremental export from DynamoDB to S3 using AWS CDK, creating a Lambda function triggered daily by an EventBridge rule to ensure seamless data export, preventing data loss and providing timely access for stakeholders.}
        \resumeItem{Actively led multiple stakeholder demonstrations of project deliverables, showcasing functionalities and impact while engaging with feedback to drive further improvements and ensure alignment with project goals.}
        \resumeItem{Established unit testing best practices, creating comprehensive documentation that outlines standards for consistency across various packages, enhancing code quality and facilitating collaboration among team members.}
      \resumeItemListEnd

    \resumeSubheading%DONE
      {IT Technician}{February 2022 -- December 2022}
      {University of Nevada, Las Vegas}{Las Vegas, NV}
      \resumeItemListStart
        \resumeItem{Developed a web application using C\# and .NET with Selenium to scrape data from solar energy websites.}
        \resumeItem{Implemented the application as a background service, periodically updating Google Spreadsheets and providing the latest solar energy data for staff on the facilities website.}
        \resumeItem{Resolved hardware and software issues by managing support tickets for university facilities.}
        \resumeItemListEnd

    \resumeSubheading%DONE
      {Software Development Engineer Intern}{May 2022 -- August 2022}
      {Amazon}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Developed and delivered a feature for an internal tool, enhancing the image management process for Treasure Truck badges in the Detail Page Experience.}
        \resumeItem{Integrated internal services and database tools using Angular/TypeScript and Java RESTful APIs to implement seamless CRUD operations, ensuring compatibility and enhancing product workflows.}
        \resumeItem{Ensured code quality and system reliability through manual, automated, and unit testing using JUnit.}
        \resumeItem{Led the team as Scrum Master, facilitating meetings, overseeing sprint progress, and tracking task deadlines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading%DONE
          {\textbf{CommUNI} $|$ \emph{JavaScript, React, Firebase, Git}}{August 2022 -- October 2022}
          \resumeItemListStart
            \resumeItem{Developed a React-based web application as part of a 10-member capstone project team, facilitating task delegation and supporting team members in their roles.}
            \resumeItem{Designed and implemented features that enhanced student communication and coordination, improving event planning.}
          \resumeItemListEnd
      \resumeProjectHeading%DONE
        {\textbf{EMPOWER UNLV} $|$ \emph{JavaScript, HTML, CSS}}{December 2021 -- May 2022}
          \resumeItemListStart
            \resumeItem{Collaborated with the Oh Lab of Neurogenetics and Precision Medicine as part of Dr. Jorge Fonseca's app development team, contributing to the creation of a website that facilitates COVID-19 variant tracking through wastewater surveillance data.}
            \resumeItem{Contributed to building the website using JavaScript, HTML, CSS, and Bootstrap, creating a user-friendly interface that effectively kept users informed about COVID-19 variants.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C/C++/C\#, HTML/CSS} \\
     \textbf{Frameworks}{: React, Angular, Node.js, JUnit, JSP, Agile} \\
     \textbf{AWS Services}{: CDK, Lambda, SageMaker, Glue, DynamoDB, CloudWatch} \\
     \textbf{Developer Tools}{: Git, VS Code, IntelliJ} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
